%-------------------------
% Resume in LateX
% Author : Dmitri Manajev
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItemPrj}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingInfo}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \small #5
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItemPrj{#1}{#2}\vspace{-4pt}}

% One-line cert/training item with right-aligned date/status
\newcommand{\resumeCertItem}[2]{ 
  \item\small{ 
    \textbf{#1} \,--\, \textit{#2}\vspace{-6pt} 
  } 
}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://manajev.com/}{\Large Dmitri Manajev}} & Email: \href{mailto:dmitri@manajev.com}{dmitri@manajev.com}\\
  Zurich, Switzerland / Remote & Github: \href{https://github.com/legalaspro}{github.com/legalaspro} \\
  \href{https://manajev.com/}{manajev.com} & Linkedin: \href{https://linkedin.com/in/dmitri-manajev/}{linkedin.com/in/dmitri-manajev} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Reinforcement Learning \& Robotics engineer with \textbf{12+ years} of engineering experience shipping production software.
Build multi-agent \& continuous-control systems: MAPPO, HAPPO, MADDPG, PPO, SAC, TD3 in PyTorch,
Unity ML-Agents, ROS~2/C++. Focus on reproducible training, evaluation and deployment 
(Docker, CI), deployable control, and hands-on real-robot lab work - 
spanning \textit{autonomous agents, planning/control, sim-to-real, and experimentation tooling}.

% --------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{RL}
      {  PPO, SAC, TD3, TRPO, A2C/A3C, DDPG, MAPPO, HAPPO, MADDPG; multi-agent (PettingZoo, SMACv2)}
    \resumeSubItem{Robotics}
      { ROS, ROS~2; C++; URDF, Xacro; tf/tf2 (ROS transforms); Nav2, MoveIt 2; MuJoCo, Gazebo, Isaac Gym; sim-to-real, continuous control}
    \resumeSubItem{AI/ML/Tools}
      { PyTorch (primary), JAX, TensorFlow, NumPy, OpenCV, Weights \& Biases, Unity ML-Agents}
    \resumeSubItem{Infra}
      { Docker, Git, Linux, AWS, Jenkins}
    \resumeSubItem{Languages \& Other}
      { Python, C++, JavaScript, Swift, SQL, Solidity, Node.js, EVM}
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    
    \resumeSubItem{\href{https://github.com/legalaspro/marl-ppo-suite}{MARL PPO Suite}}
      {MAPPO/HAPPO for cooperative MARL (SMACv2); clean training/eval pipeline.
      \textit{Proof:} \href{https://wandb.ai/legalaspro-rl/marl-ppo-suite/reports/MAPPO-vs-HAPPO-SMACv2-Benchmarks---VmlldzoxMjY1NjYwMg}{W\&B benchmarks}, \href{https://huggingface.co/models?other=marl-ppo-suite}{HF Model Zoo}.}

    \resumeSubItem{\href{https://github.com/legalaspro/unity_multiagent_rl}{Unity Multi-Agent RL}}
      {MAPPO/MASAC/MATD3/MADDPG with evaluation tooling; demonstrated performance on Unity Tennis/Soccer.}

    \resumeSubItem{\href{https://github.com/legalaspro/maddpg-zoo-torch}{MADDPG Zoo (PyTorch)}}
      {Modern MADDPG for PettingZoo; reproducible baselines and evaluation scripts.}

    \resumeSubItem{\href{https://github.com/legalaspro/rl-odyssey}{RL-Odyssey}}
      {Continuous-control RL (DDPG/TD3/SAC/PPO/TRPO/A2C/A3C) with notebooks \& scripts.}

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Manajev AI Labs (independent)}{Zurich, CH}
      {AI/RL/Robotics Specialist}{Dec 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Build reproducible RL training and evaluation pipelines for multi-agent \& continuous control (MAPPO/HAPPO, MADDPG, PPO/SAC/TD3) on Unity ML-Agents/PettingZoo.}
        \resumeItem{Prototype ROS~2/C++ control loops for policy integration; containerized environments for on-device runs.}
        \resumeItem{Run algorithmic benchmarks and publish artifacts (W\&B reports, HF model zoo).}
        \resumeItem{Hands-on lab work with a differential-drive mobile base and a 6-DoF manipulator + gripper; navigation, waypointing, and basic manipulation in sim and ROS~2.}
      \resumeItemListEnd
      
    \resumeSubheading
      {CryptoApps Manajev}{Zurich, CH}
      {Founder \& Engineer}{2018 -- 2024}
      \resumeItemListStart
        \resumeItem{Shipped full-stack blockchain apps (Solidity/Node/Vue) and performed smart-contract reviews \& security testing.}
        \resumeItem{Developed MEV-aware transaction routing and automation; optimized node infrastructure for cost/latency.}
      \resumeItemListEnd
  
    % Swissmeda — Role 1
    \resumeSubheading
      {Swissmeda AG}{Zurich, CH}
      {Product \& IT Manager / Architect / DevOps}{2015 -- 2018}
      \resumeItemListStart
        \resumeItem{ Managed remote engineering team, led migration to AWS/Linux/GitHub/Jira/Confluence; standardized CI/CD (Jenkins/Fastlane).}
        \resumeItem{ Designed cloud infrastructure (AWS CFN/Ansible) and release pipelines across multi-brand apps. }
        \resumeItem{ Authored product specs/PRDs; aligned regulatory constraints; drove iOS \& backend releases.}
        \resumeItem{ Architected and shipped the \textbf{smop} iOS app for 3D implant plan review; improved release cadence \& reliability \href{https://apps.apple.com/us/app/smop/id971741467}{\textbf{App Store}}.}
      \resumeItemListEnd

    % Swissmeda — Role 2 (separate entry)
    % Some parsers have problem parsing 2 job roles for same company
    \resumeSubheading
      {Swissmeda AG}{Zurich, CH}
      {Senior iOS Engineer}{2014 -- 2015}
      \resumeItemListStart
        \resumeItem
         {Architected the multi-brand \href{https://apps.apple.com/us/app/smop/id971741467}{\textbf{smop}} iOS client; automated staging/deploy (Fastlane/CocoaPods); collaborated with surgical planning team.}
      \resumeItemListEnd
    
    \resumeSubheading
        {SpotMe (Shockfish SA)}{Lausanne, CH}
        {Full-Stack Engineer}{2013 -- 2014}
        \resumeItemListStart
            \resumeItem{Built real-time event features (voting, photo sharing, check-in, surveys, data viz) across backend \& mobile web (Node, CouchDB, d3).}
        \resumeItemListEnd
    
    \resumeSubheading
      {Life Ideas}{St. Petersburg, RU}
      {Creator}{2012 -- 2013}
      \resumeItemListStart
          \resumeItem{ Created \textbf{Instacam} (Windows Phone 7 Instagram client); received media coverage and broad user adoption \href{https://www.redmondpie.com/instagram-for-windows-phone-7-is-unofficially-here/}{\textbf{press}}. }
      \resumeItemListEnd
    
    \resumeSubheading
      {Lanit-Tercom}{St. Petersburg, RU}
      {Software Engineer}{2010 -- 2012}
      \resumeItemListStart
          \resumeItem{ WPF/.NET, mobile/web; GUI + backend development.}
      \resumeItemListEnd

   
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingInfo
      {St. Petersburg State University(SPbSU)}{St. Petersburg, Russia}
      {Specialist / M.S. in Software Engineering \& Mathematics}{2007 -- 2012}
      {\textbf{Thesis}: Collaborative recommendation system for tourist attractions.}
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS \& TRAINING-----------------
\section{Certifications \& Training}
  \resumeSubHeadingListStart
    \resumeCertItem{\href{https://www.theconstruct.ai/robotics-developer/}{Robotics Developer (Masterclass), The Construct}}{In progress — Sep--Dec 2025}
    \resumeCertItem{\href{https://www.theconstruct.ai/unitree-g1-humanoid-robotics-certificate-training/}{Humanoid Robotics Certificate (Barcelona), The Construct}}{Scheduled — Dec 10--12, 2025}
    \resumeCertItem{\href{https://www.udacity.com/certificate/e/a3bacae8-bb66-11ed-826d-cbcb7e7fecc7}{Deep Reinforcement Learning (Nanodegree), Udacity}}{2025}
    \resumeCertItem{\href{https://www.udacity.com/certificate/e/6c29da6e-75b7-11ed-b96b-671d91689ee6}{Machine Learning with PyTorch (Nanodegree), Udacity}}{2023}
    \resumeCertItem{\href{https://www.udacity.com/certificate/e/9ff0fd60-75b6-11ed-984e-53126f988a5f}{Full Stack JavaScript Developer (Nanodegree), Udacity}}{2023}
    \resumeCertItem{\href{https://www.udacity.com/certificate/e/7d6c9ede-5fc5-11ef-b8e4-0bf0243c348f}{Data Analysis with Pandas \& NumPy, Udacity}}{2023}
 
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}



